Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-11 WRITEUP/ms.tex
update fig 3, resize fig, finished sec 5, finished sec 3.2.1 on MR relation, polished more

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted,
with $\sigma\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures.
The high velocity dispersions likely result from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the intergalactic medium.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
mass distribution, which steepens with $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

This paper is structured as follows.
\AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
We note that, owing to the nature of \obs, such structures are identified 
in position-position-velocity (PPV) space, whereas in simulations, one has the 
full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in
PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
Pan15a, Ibanez-Mejia16a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.png}
  \\[-5.5em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.png}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
	Color shows the H$_2$ surface density, weighted by the column density. Specifically, this is calculated using \Eq{integrate}.
	\AP{additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

@@

For visualization, we overplot the molecular structures identified using
a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps 
in \Fig{MC} as an example.
The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
\begin{equation}
{\rm voxel_i} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
\label{eqn:integrate}
\end{equation} 
where $\rho_{\rm H2, i}$ is the H$_2$ density of voxel $i$, $w_i$ is the weighted quantity in voxel $i$ which we adopt 
to be the total gas density, and $\Delta z_i$ is the path length of voxel $i$ along the line-of-sight over which the quantities are integrated along.

@@

\AP{I see 2 main possible approaches to the presentation of the results
%
(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
%
(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
%
Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
%
I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g. the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
}
\DL{agreed, but will move things around later, after the report and after most of the content is ready.}

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
% {\AP The size is an effective radius, calculated from the total volume of the MC assuming spherical symmetry.}
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
which is summed over the cells composing each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

@@

The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
which are supported by turbulence and rotation. 
In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
the MC itself is gravitationally unbound and is supported/confined 
by turbulence (from the feedback of multiple episodes of \SF) 
and galactic rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way 
(other symbols).
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
\label{fig:alpha27}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified across all snapshots. 
Star symbols are color-coded by increasing SFR.
\label{fig:alpha16-28}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
(i.e., MCs here are identified with the highest $n_{\rm cut}$).
\label{fig:alpha16-28-highncut}}
\end{figure}

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales 
via two physical properties: mass and size \citep{Larson81a, Mckee07a}. This is also known as the law of constant column density, 
since cloud mass in \obs is sometimes derived by integrating
over the mass surface density ($\Sigma$), which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).   
That is, $N_{\rm H2}\propto A_V$, $\Sigma\propto N_{\rm H2}$, and $M$\eq$\int \Sigma~dA$.
Therefore, cloud mass is related to $N_{\rm H2}$ and $A_V$.

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accretion phase (see \Sec{sfh})
compared to the 
observational data of molecular clouds in the Milky Way associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
{\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accretion phase. 
{\bf so...}

Similar MC properties in relation to those observed in the nearby Universe are found for \flower in its starburst phase (see bottom 
panel of \Fig{larsons_single} and \Fig{alpha27}).
% 
% \subsubsection{Temporal Evolution in Cloud Dynamics}
% What about all snapshots, where should the results for that go... \Fig{alpha16-28}, \Fig{larsons16-28}, \Fig{larsons16-28-highncut} and \Fig{alpha16-28-highncut}.

@@

The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
consistent with those observed in \z$\sim$2 galaxies in
rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
Observational studies in the nearby Universe, where 
spatially resolution are better at revealing molecular (sub-)structures,
often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
While the CMF of the MCs for a given snapshot of our simulation is 
quite noisy, since we have only one (main) galaxy, 
we can improve the ``signal-to-noise ratio'' by including 
MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We use a clump-finding algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted,
with $\sigma\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures.
The high velocity dispersions likely result from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the intergalactic medium.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
mass distribution, which steepens with $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

This paper is structured as follows.
% \AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular clouds
and structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q}.
We discuss the results % , robustness of our analysis, caveats, 
and implications of our findings in \Sec{diss},
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\subsection{Structure identification} \label{sec:method}
To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree). It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles. 
In the customized version used for this study, we modify the function to enhance the stability of the code.
% (which essentially means we fixed the bugs in order for it to actually work).

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
We note that, owing to the nature of \obs, such structures are identified 
in position-position-velocity (PPV) space, whereas in simulations, one has the 
full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical properties extracted in
PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em] 
  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
	Color shows the H$_2$ surface density, weighted by the column density. Specifically, this is calculated using \Eq{integrate}.
% 	\AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear... hmm.. Not worth my time to fix this for the report.}
\label{fig:MC}}
% \addtocounter{figure}{-1}
\end{figure*}

@@

For visualization, we overplot the molecular structures identified using
a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps 
in \Fig{MC} as an example.
The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
\begin{equation}
{\rm pixel_i} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
\label{eqn:integrate}
\end{equation} 
where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.

@@

%\AP{I see 2 main possible approaches to the presentation of the results
%%
%(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
%%
%(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
%%
%Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
%%
%I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g. the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
%}
%\DL{agreed, but will move things around later, after the report and after most of the content is ready.}

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field,
integrating over all zones of the MC, multiplied by its volume. 
The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
% {\AP The size is an effective radius, calculated from the total volume of the MC assuming spherical symmetry.}
Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
the non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
which is summed over the cells composing each MC.
The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\end{equation}
The local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion ($\sigma$).}.
On average, the Mach number of the MCs corresponds to about $\mathcal{M}\approx50$.
This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

@@

The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
which are supported by turbulence and rotation. 
In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
the MC itself is gravitationally unbound and is supported
by turbulence (from the feedback of multiple episodes of \SF) 
and galactic rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way 
(other symbols).
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
\label{fig:alpha27}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified across all snapshots. 
Star symbols are color-coded by increasing SFR.
\label{fig:alpha16-28}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
(i.e., MCs here are identified with the highest $n_{\rm cut}$).
\label{fig:alpha16-28-highncut}}
\end{figure*}

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales 
via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the law of constant column density, 
since cloud mass in \obs is sometimes derived by integrating
over the mass surface density ($\Sigma$), which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).   
That is, $N_{\rm H2}\propto A_V$, $\Sigma\propto N_{\rm H2}$, and $M$\eq$\int \Sigma~dA$.
Therefore, cloud mass is related to $N_{\rm H2}$ and $A_V$.

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accretion phase (see \Sec{sfh})
compared to the 
observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein).
This relation is obtained by comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun). 
\citet{Kauffmann10c} interpret this
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as
the threshold for massive \SF.
The implication of this result is that cluster-forming cloud fragments are 
found to be more massive than those that are devoid of clusters 
at a given radius.

As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}, which 
% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
is below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
This can be understood by acknowledging the fact that a H$_2$ molecular cloud 
does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
and that our simulation does not have enough resolution to directly form CO\footnote{
In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we 
model the internal structure of MC within each cell in our simulation.}.
That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the 
fact that the MCs in our simulation have lower column density compared to the star-forming cores observed in the Milky Way, which are 
observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
% unresolved CO?detected molecular clouds in other galaxies should have an average A_V = 4 mag.

Similar MC properties in relation to those observed in the nearby Universe are found during the starburst phase of 
\flower (see e.g., bottom panel of \Fig{larsons_single} and \Fig{alpha27}).
On average, we do not find any quantitative differences in the MC properties in the accretion versus starburst phase.

@@

The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, which is
consistent with those observed in \z$\sim$2 galaxies in
rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
Observational studies in the nearby Universe, where 
spatially resolution are better at revealing molecular (sub-)structures,
often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
While the CMF of the MCs for a given snapshot of our simulation is 
quite noisy, since we have only one (main) galaxy, 
we can improve the ``signal-to-noise ratio'' by including 
MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.
